---
title: ""
format: 
  revealjs:
    theme: [default, customizations/presentation-custom.scss]
    logo: static/noaa-fisheries-logo.png
    css: customizations/logo.css
    slide-number: true
    cap-location: top
    smaller: true
    plugins: [mermaid]
    mermaid:
      format: svg
embed-resources: true
params: 
  endyr: 2025
editor: 
  markdown: 
    wrap: 72
---

#  {.center}

::: {.titlebox style="text-align:center; font-size: 1.25em;"}
[Pelagic Fish Data Report `r params$endyr`]{.blue-title}

[Pacific Islands Fisheries Science Center]{.blue
style="font-size:0.5em;"} <br> [Fisheries Research and Monitoring
Division]{.blue style="font-size:0.5em;"}
:::

<!---This is how to add comments to a quarto file--->

## Vessels by Fleet

```{r}
#| echo: false
#| warning: false
#| fig-height: 5.5
#| fig-width: 9

source(file.path("graphs.r"))
vessels_by_fleet

```

## Catch by Fleet in Metric Tons

```{r}
#| echo: false
#| warning: false
#| fig-width: 13.5
#| fig-height: 7.5

totals_by_fleet

```

## Catch by Species in Metric Tons

```{r}
#| echo: false
#| warning: false
#| fig-width: 18
#| fig-height: 10

totals_by_species

```

::: key
Species key: ALB = albacore, ALV = common thresher shark, BET = bigeye
tuna, BIL = other billfish, BSH = blue shark, BTH = bigeye thresher
shark, BUM = blue marlin, MLS = striped marlin, PBF = Pacific bluefin
tuna, PTH = pelagic thresher shark, SKH = other sharks, SKJ = skipjack
tuna, SMA = shortfin mako shark, SWO = swordfish, TUN = other tunas, YFT
= yellowfin tuna
:::

## Relative Frequency of Catch [(2020–2024)]{.fragment data-fragment-index="1" style="font-size: 25px;"}

::::: r-stack
::: {.fragment .fade-out fragment-index="1"}
```{r}
#| echo: false
#| warning: false
#| fig-height: 10
#| fig-width: 18

frequency_by_fishery

```
:::

::: {.fragment .fade-in fragment-index="1"}
```{r}
#| echo: false
#| warning: false
#| fig-height: 10
#| fig-width: 18

recent_frequency_by_fishery

```
:::
:::::

::: key
Species key: ALB = albacore, BET = bigeye tuna, BSH = blue shark, BUM =
blue marlin, MLS = striped marlin, PBF = Pacific bluefin tuna, SKJ =
skipjack tuna, SMA = shortfin mako shark, SWO = swordfish, YFT =
yellowfin tuna
:::

## Relative Frequency of Catch [(2020–2024)]{.fragment data-fragment-index="1" style="font-size: 25px;"}

::::: r-stack
::: {.fragment .fade-out fragment-index="1"}
```{r}
#| echo: false
#| warning: false
#| fig-height: 10
#| fig-width: 18

frequency_by_species

```
:::

::: {.fragment .fade-in fragment-index="1"}
```{r}
#| echo: false
#| warning: false
#| fig-height: 10
#| fig-width: 18

recent_frequency_by_species

```
:::
:::::

::: key
Species key: ALB = albacore, BET = bigeye tuna, BSH = blue shark, BUM =
blue marlin, MLS = striped marlin, PBF = Pacific bluefin tuna, SKJ =
skipjack tuna, SMA = shortfin mako shark, SWO = swordfish, YFT =
yellowfin tuna
:::

## Longline Catch

```{r}
#| echo: false
#| warning: false
#| fig-height: 7.5
#| fig-width: 13.5

longline_prop
```


## Purse Seine Catch
::::: columns
:::{.column width="72%"}
```{r}
#| echo: false
#| warning: false
#| fig-height: 7
#| fig-width: 8.5

purse_seine_prop

```
:::

:::{.column width="28%" .scroll}
```{r}
#| echo: false

purse_seine_table %>% gt() %>%
  fmt_number(columns = !contains("Year"), decimals=0) %>% 
  fmt_number(columns = contains(c("ALB", "BET", "SKJ", "Total")), suffixing=TRUE, n_sigfig=3) %>% 
  cols_align("center", everything()) %>%
  tab_style(
    style = cell_text(size = px(12), weight = "bold", align = "center"),
    locations = cells_column_labels()
  ) %>% 
  tab_style(
    style = cell_text(size = px(12), align = "right"),
    locations = cells_body()
  ) #%>% 
  #cols_width(
   # contains("Total") ~ px(40)
  #) %>% 
  #cols_width(
   # contains("Year") ~ px(35)
  #)
```
:::
:::::

::: key
Species key: ALB = albacore, BET = bigeye tuna, PBF = pacific bluefin tuna, SKJ = skipjack tuna, YFT = yellowfin tuna
:::

## Tropical Troll Catch
::::: columns
:::{.column width="72%"}
```{r}
#| echo: false
#| warning: false
#| fig-height: 7
#| fig-width: 8.5

tropical_troll_prop

```
:::

:::{.column width="28%" .scroll}
```{r}
#| echo: false

tropical_troll_table %>% gt() %>%
  fmt_number(columns = !contains("Year"), decimals=0) %>% 
  cols_align("center", everything()) %>%
  tab_style(
    style = cell_text(size = px(12), weight = "bold", align = "center"),
    locations = cells_column_labels()
  ) %>% 
  tab_style(
    style = cell_text(size = px(12), align = "right"),
    locations = cells_body()
  ) 
```
:::
:::::

::: key
Species key: ALB = albacore, BET = bigeye tuna, PBF = pacific bluefin
tuna, YFT = yellowfin tuna
:::

## Sport Catch

::::: columns
::: {.column width="75%"}
```{r}
#| echo: false
#| warning: false
#| fig-height: 6.5
#| fig-width: 8.5

sport_prop

```
:::

::: {.column .scroll width="25%"}
```{r}
#| echo: false

sport_table %>% gt() %>%
  fmt_number(columns = !contains("Year"), decimals = 0) %>% 
  cols_align("center", everything()) %>%
  tab_style(
    style = cell_text(size = px(14), weight = "bold", align = "center"),
    locations = cells_column_labels()
  ) %>% 
  tab_style(
    style = cell_text(size = px(14), align = "right"),
    locations = cells_body()
  ) %>% 
  cols_width(
    contains("Total") ~ px(45)
  ) %>% 
  cols_width(
    contains("Year") ~ px(40)
  )

```
:::
:::::

::: key
Species key: ALB = albacore, MLS = striped marlin, PBF = pacific bluefin
tuna, YFT = yellowfin tuna
:::

::::: columns
:::
## Yellowfin Tuna Catch

```{r}
#| echo: false
#| warning: false
#| fig-height: 7.5
#| fig-width: 13.5


yellowfin_prop
```

## Pacific Bluefin Tuna Catch

```{r}
#| echo: false
#| warning: false
#| fig-height: 7.5
#| fig-width: 13.5

bluefin_prop

```

## All Species Catch

```{r}
#| echo: false
#| warning: false
#| fig-height: 7.5
#| fig-width: 13.5

all_species_prop

```